---
title: "Assignment5"
author: "Kristin Gmunder"
date: "2/17/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

A patient has a rare disease where P(having disease)=0.001.  Using the binomial distribution to find the probability of accruing 0 patients if interviewing 400.
```{r}
choose(400,0)*(0.001^0)*(0.999^400)
```
There is a probability of 67% that if 400 patients are interviewed, 0 will have disease.

A patient has a less rare disease where P(having disease)=0.05.  Modeling the probability of finding 150 patients when we check 10,000 charts using negative binomial.
```{r}
choose(10149, 10000)*((0.95)^150)*((0.05)^10000)
```
It appears that this calculation seems to be beyond R's range for both the choose function and the factorial function.  So I receive an answer of infinity for the first term, thus this probability cannot be calculated.


Using the geometric distribution to find the probability of interviewing 20 subjects until seeing the first patient with disease (same probability of disease within the population as before).
```{r}
(.05)*(0.95)^20
```
With a probability of 1.79% it is very unlikely that we will find a patient with disease in the first 20 people interviewed.
