---
title: "Assignment9"
author: "Kristin Gmunder"
date: "4/4/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Question 1**  
Plot a N(0, 1) density and histogram with 10,000 samples from the normal distribution.
```{r}
n_10000 <- rnorm(n = 10000, mean = 0, sd = 1)
hist(n_10000, xlim=c(-10, 10))
plot(density(n_10000), xlim=c(-10, 10))
```

**Question 2**  
Plot a density and histogram with 10,000 samples from the t distribution with 3, 8, 15, 30, and 100 degrees of freedom.
```{r}
t3_10000 <- rt(n = 10000, df = 3)
hist(t3_10000, xlim=c(-10, 10))
plot(density(t3_10000), xlim=c(-10, 10))

t8_10000 <- rt(n = 10000, df = 8)
hist(t8_10000, xlim=c(-10, 10))
plot(density(t8_10000), xlim=c(-10, 10))

t15_10000 <- rt(n = 10000, df = 15)
hist(t15_10000, xlim=c(-10, 10))
plot(density(t15_10000), xlim=c(-10, 10))

t30_10000 <- rt(n = 10000, df = 30)
hist(t30_10000, xlim=c(-10, 10))
plot(density(t30_10000), xlim=c(-10, 10))

t100_10000 <- rt(n = 10000, df = 100)
hist(t100_10000, xlim=c(-10, 10))
plot(density(t100_10000), xlim=c(-10, 10))
```
As the degrees of freedom increase in the t-distribution, it approaches the nnormal distribution.

**Question 3**  
Plot a density and histogram with 10,000 samples from the F distribution with 4 different values of $\nu_1$ and $\nu_2$.
```{r}
F33_10000 <- rf(n = 10000, df1 = 3, df2 = 3)
hist(F33_10000, xlim=c(-10, 10))
plot(density(F33_10000), xlim=c(-10, 10))

F38_10000 <- rf(n = 10000, df1 = 3, df2 = 8)
hist(F38_10000, xlim=c(-10, 10))
plot(density(F38_10000), xlim=c(-10, 10))

F315_10000 <- rf(n = 10000, df1 = 3, df2 = 15)
hist(F315_10000, xlim=c(-10, 10))
plot(density(F315_10000), xlim=c(-10, 10))

F330_10000 <- rf(n = 10000, df1 = 3, df2 = 30)
hist(F330_10000, xlim=c(-10, 10))
plot(density(F330_10000), xlim=c(-10, 10))

F88_10000 <- rf(n = 10000, df1 = 8, df2 = 8)
hist(F88_10000, xlim=c(-10, 10))
plot(density(F88_10000), xlim=c(-10, 10))

F815_10000 <- rf(n = 10000, df1 = 8, df2 = 15)
hist(F815_10000, xlim=c(-10, 10))
plot(density(F815_10000), xlim=c(-10, 10))

F830_10000 <- rf(n = 10000, df1 = 8, df2 = 30)
hist(F830_10000, xlim=c(-10, 10))
plot(density(F830_10000), xlim=c(-10, 10))

F3030_10000 <- rf(n = 10000, df1 = 30, df2 = 30)
hist(F3030_10000, xlim=c(-10, 10))
plot(density(F3030_10000), xlim=c(-10, 10))
```


