---
title: "Assignment2"
author: "Kristin Gmunder"
date: "1/23/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Advanced R: Functions

####Function Components
``` {r}
f <- function(x) x^2
f
#> function(x) x^2

formals(f)
#> $x
body(f)
#> x^2
environment(f)
```

####Primitive Functions
```{r}
sum
## function (..., na.rm = FALSE)  .Primitive("sum")
formals(sum)
## NULL
body(sum)
## NULL
environment(sum)
## NULL
```

####Exercises 1
**1. What function allows you to tell if an object is a function? What function allows you to tell if a function is a primitive function?**
str() will tell you if an object is a function.  If body() of function returns NULL then this function is primitive.

**2. This code makes a list of all functions in the base package.**
```{r}
objs <- mget(ls("package:base"), inherits = TRUE)
funs <- Filter(is.function, objs)
```
**Use it to answer the following questions: Which base function has the most arguments? How many base functions have no arguments? What’s special about those functions? How could you adapt the code to find all primitive functions?**
scan() has the most arguments. 221 have no aruments.

**What are the three important components of a function?**
body(), formals(), environment()

**When does printing a function not show what environment it was created in?**
If it is a primitive function, the environment will be NULL.

####Lexical Scoping
```{r}
x <- 10
x

```

####Name Masking
```{r}
f <- function() {
  x <- 1
  y <- 2
  c(x, y)
}
f()
rm(f)

f <- function() {
  x <- 1
  y <- 2
  c(x, y)
}
f()
rm(f)

x <- 1
h <- function() {
  y <- 2
  i <- function() {
    z <- 3
    c(x, y, z)
  }
  i()
}
h()
rm(x, h)

j <- function(x) {
  y <- 2
  function() {
    c(x, y)
  }
}
k <- j(1)
k()
rm(j, k)
```

####Functions vs. variables
```{r}
l <- function(x) x + 1
m <- function() {
  l <- function(x) x * 2
  l(10)
}
m()
rm(l, m)
n <- function(x) x / 2
o <- function() {
  n <- 10
  n(n)
}
o()
rm(n, o)
```

####A Fresh Start
```{r}
j <- function() {
  if (!exists("a")) {
    a <- 1
  } else {
    a <- a + 1
  }
  a
}
j()
rm(j)
```

####Dynamic Lookup

f <- function() x
x <- 15
f()

x <- 20
f()

f <- function() x + 1
codetools::findGlobals(f)

environment(f) <- emptyenv()
f()

`(` <- function(e1) {
  if (is.numeric(e1) && runif(1) < 0.1) {
    e1 + 1
  } else {
    e1
  }
}
replicate(50, (1 + 2))
rm("(")


####Exercises
**1. What does the following code return? Why? What does each of the three c’s mean?**
```{r}
c <- 10
c(c = c)
```
The code returns:
c
10
This is because the first c concatatenates a vector where the second c equals the already assigned value of 10 for the third c.

**2.What are the four principles that govern how R looks for values?**
The four principles are name masking, functions vs. variables, a fresh start, and dynamic lookup.

**3.What does the following function return? Make a prediction before running the code yourself.**
```{r}
f <- function(x) {
  f <- function(x) {
    f <- function(x) {
      x ^ 2
    }
    f(x) + 1
  }
  f(x) * 2
}
f(10)
```
The following function returns 202.

####Every Operation is a Function Call
```{r}
x <- 10; y <- 5
x + y

`+`(x, y)

for (i in 1:2) print(i)

`for`(i, 1:2, print(i))

if (i == 1) print("yes!") else print("no.")

`if`(i == 1, print("yes!"), print("no."))

x[3]

`[`(x, 3)

{ print(1); print(2); print(3) }

`{`(print(1), print(2), print(3))

add <- function(x, y) x + y
sapply(1:10, add, 3)

sapply(1:5, `+`, 3)

sapply(1:5, "+", 3)

x <- list(1:3, 4:9, 10:12)
sapply(x, "[", 2)

sapply(x, function(x) x[2])
```

####Calling Functions

f <- function(abcdef, bcde1, bcde2) {
  list(a = abcdef, b1 = bcde1, b2 = bcde2)
}
str(f(1, 2, 3))

str(f(2, 3, abcdef = 1))

str(f(2, 3, a = 1))

str(f(1, 3, b = 1))

mean(1:10)
mean(1:10, trim = 0.05)

mean(x = 1:10)

mean(1:10, n = T)
#mean(1:10, , FALSE)
mean(1:10, 0.05)
#mean(, TRUE, x = c(1:10, NA))
```

####Calling a function given a list of arguments
```{r}
args <- list(1:10, na.rm = TRUE)

do.call(mean, args)

mean(1:10, na.rm = TRUE)
```

####Default and Missing Arguments
```{r}
f <- function(a = 1, b = 2) {
  c(a, b)
}
f()

g <- function(a = 1, b = a * 2) {
  c(a, b)
}
g()

g(10)

h <- function(a = 1, b = d) {
  d <- (a + 1) ^ 2
  c(a, b)
}
h()

h(10)

i <- function(a, b) {
  c(missing(a), missing(b))
}
i()

i(a = 1)

i(b = 2)

i(1, 2)
```

####Lazy Arguments

f <- function(x) {
  10
}

f(stop("This is an error!"))

f <- function(x) {
  force(x)
  10
}
f(stop("This is an error!"))

add <- function(x) {
  function(y) x + y
}
adders <- lapply(1:10, add)
adders[[1]](10)

adders[[10]](10)

add <- function(x) {
  force(x)
  function(y) x + y
}
adders2 <- lapply(1:10, add)
adders2[[1]](10)

adders2[[10]](10)

add <- function(x) {
  x
  function(y) x + y
}

f <- function(x = ls()) {
  a <- 1
  x
}

f()

f(ls())

x <- NULL
if (!is.null(x) && x > 0) {

}

`&&` <- function(x, y) {
  if (!x) return(FALSE)
  if (!y) return(FALSE)

  TRUE
}
a <- NULL
!is.null(a) && a > 0

if (is.null(a)) stop("a is null")

!is.null(a) || stop("a is null")

plot(1:5, col = "red")
plot(1:5, cex = 5, pch = 20)

plot(1:5, bty = "u")
plot(1:5, labels = FALSE)

f <- function(...) {
  names(list(...))
}
f(a = 1, b = 2)

sum(1, 2, NA, na.mr = TRUE)
```

####Exercises
**1. Clarify the following list of odd function calls:**
```{r}
x <- sample(replace = TRUE, 20, x = c(1:10, NA))
#x <- sample(x= c(1:10,NA), size=20, replace=TRUE)
y <- runif(min = 0, max = 1, 20)
#y <-runif(n = 20, min = 0, max = 1)
cor(m = "k", y = y, u = "p", x = x)
#cor(x=x, y=y, use="pairwise.complete.obs", method = "kendall")
```

**2. What does this function return? Why? Which principle does it illustrate?**
```{r}
f1 <- function(x = {y <- 1; 2}, y = 0) {
  x + y
}
f1()
```
Function returns 3 and illustrates the principle of name masking.

**3. What does this function return? Why? Which principle does it illustrate?**
```{r}
f2 <- function(x = z) {
  z <- 100
  x
}
f2()
```
Function returns 100 and illustrates the principle of dynamic evaluation.

####Infix Functions
```{r}
`%+%` <- function(a, b) paste0(a, b)
"new" %+% " string"

"new" %+% " string"

`%+%`("new", " string")

1 + 5

`+`(1, 5)

`% %` <- function(a, b) paste(a, b)
`%'%` <- function(a, b) paste(a, b)
`%/\\%` <- function(a, b) paste(a, b)

"a" % % "b"

"a" %'% "b"

"a" %/\% "b"

`%-%` <- function(a, b) paste0("(", a, " %-% ", b, ")")
"a" %-% "b" %-% "c"

`%||%` <- function(a, b) if (!is.null(a)) a else b
#function_that_might_return_null() %||% default value
```

####Replacement Functions

`second<-` <- function(x, value) {
  x[2] <- value
  x
}
x <- 1:10
second(x) <- 5L
x

library(pryr)
x <- 1:10
address(x)

second(x) <- 6L
address(x)

x <- 1:10
address(x)

x[2] <- 7L
address(x)

`modify<-` <- function(x, position, value) {
  x[position] <- value
  x
}
modify(x, 1) <- 10
x

x <- `modify<-`(x, 1, 10)

modify(get("x"), 1) <- 10

get("x") <- `modify<-`(get("x"), 1, 10)

x <- c(a = 1, b = 2, c = 3)
names(x)

names(x)[2] <- "two"
names(x)

`*tmp*` <- names(x)
`*tmp*`[2] <- "two"
names(x) <- `*tmp*`
```

####Exercises
**1. Create a list of all the replacement functions found in the base package. Which ones are primitive functions?**
**2. What are valid names for user-created infix functions?**
Functions that start and end with %.

**3. Create an infix xor() operator.**
```{r}
`%xor%` <- function(x,y) {
  xor(x,y)
}
```

**4. Create infix versions of the set functions intersect(), union(), and setdiff().**
```{r}
`%intersect%` <- function(x, y)
{
  intersect(x, y)
}

`%union%` <- function(x, y)
{
  union(x, y)
}

`%setdiff%` <- function(x, y)
{
  setdiff(x, y)
}
```
**5. Create a replacement function that modifies a random location in a vector.**
```{r`}
`random<-` <- function(x, value) {
  x[7] <- value
  x
}
```

####Return Values
```{r}
f <- function(x) {
  if (x < 10) {
    0
  } else {
    10
  }
}
f(5)

f(15)

f <- function(x, y) {
  if (!x) return(y)
}

f <- function(x) {
  x$a <- 2
  x
}
x <- list(a = 1)
f(x)

x$a

f1 <- function() 1
f2 <- function() invisible(1)

f1()

f2()
f1() == 1

f2() == 1

(f2())

a <- 2
(a <- 2)

a <- b <- c <- d <- 2

(a <- (b <- (c <- (d <- 2))))
```

####On Exit
```{r}
in_dir <- function(dir, code) {
  old <- setwd(dir)
  on.exit(setwd(old))

  force(code)
}
getwd()

in_dir("~", getwd())
```

####Exercises
**1. How does the chdir parameter of source() compare to in_dir()? Why might you prefer one approach to the other?**
**2. What function undoes the action of library()? How do you save and restore the values of options() and par()?**
Detach() undoes library().  
**3. Write a function that opens a graphics device, runs the supplied code, and closes the graphics device (always, regardless of whether or not the plotting code worked).**
```{r}
question3 <- function()
{
  x <- 8
  y <- 10
  runif(y < x)
  plot(x, y)
  on.exit(dev.off())
}
```

**4. We can use on.exit() to implement a simple version of capture.output().**
```{r}
capture.output2 <- function(code) {
  temp <- tempfile()
  on.exit(file.remove(temp), add = TRUE)

  sink(temp)
  on.exit(sink(), add = TRUE)

  force(code)
  readLines(temp)
}
capture.output2(cat("a", "b", "c", sep = "\n"))
## [1] "a" "b" "c"
```
**Compare capture.output() to capture.output2(). How do the functions differ? What features have I removed to make the key ideas easier to see? How have I rewritten the key ideas to be easier to understand?**
capture.output() "evaluates its arguments with the output being returned as a character string or sent to a file."  Both capture.output() and capture.output2() have the same output, but they differ in how the temporary file is removed.